Catchy Part: Surveying Users' Perceptions of Threats for Wearable Devices

### 2015-01-02 wearables_survey.tex
took out within-subjects part of device analysis for results.

@@

\begin{table}%[h]
\begin{center}
\begin{tabular}{| c | c | c | c |}
%Question & Chi^2 &	2-tail P & Sig? & Odds ratio	 & Confidence& Odds range\\
%All		0.444	0.505	No	0.5		95\%			0.081 to 2.341\\
%Q1		0		1		No	n/a	         n/a	                  n/a\\
%Q2		0		1		No	0.5		95\%	                  0.008 to9.605\\
%Q3		0		1		No	n/a	         n/a	                  n/a\\
%Q4		0		1		No	0.5		95\%			0.008 to9.605\\
%Q5		0		1		No	n/a	         n/a	                  n/a\\
Question & $\chi^2$ &	2-tail P & Effect Size \\
All & 0.444  & 0.505 & 0.006\\
Q1 & 0 & 1 & 0 \\
Q2 & 0 & 1 & 0\\
Q3 & 0 & 1 & 0\\
Q4 & 0 & 1 & 0\\
Q5 & 0 & 1 & 0\\
\end{tabular}
\caption{Results of the effects of <device> type contributing to VUR. Values are McNeamar's test results for within-subjects comparisons for participants who received both questions.}
\label{withindevice}
\end{center}
\end{table}

For the between-subjects comparison (i.e., participants who received one question, but not the other), you can do either a chi-square test or Fisher's exact test. Both use a 2 x 2 contingency matrix (i.e., rows are outcomes---upset or not---and columns are conditions---wearable or smartphone). The way to choose between the two tests is based on sample size, generally you use chi-square when there are more than 10-20 samples per cell in the table, but using either is just as valid. For the within-subjects comparisons (i.e., participants received both questions), you would do McNemar's test; which is the within-subjects version of the chi-square test.

Exact question details here, and statistical stuff. Conclude with whatever conclusion I happen to come to after performing the statistical analysis.

>>>>

%%% still need to break urls

%\usepackage{breakurl}
%\usepackage[breaklinks]{hyperref}

@@

Talk about results of between-subjects analysis here.

%\begin{table}%[h]
%\begin{center}
%\begin{tabular}{| c | c | c | c |}
%Question & $\chi^2$ &	2-tail P & Effect Size \\
%All & 0.444  & 0.505 & 0.006\\
%Q1 & 0 & 1 & 0 \\
%Q2 & 0 & 1 & 0\\
%Q3 & 0 & 1 & 0\\
%Q4 & 0 & 1 & 0\\
%Q5 & 0 & 1 & 0\\
%\end{tabular}
%\caption{Results of the effects of <device> type contributing to VUR. Values are McNeamar's test results for within-subjects comparisons for participants who received both questions.}
%\label{withindevice}
%\end{center}
%\end{table}

there are too few instances where a participant got both, and therefore not enough data to really do analysis: Results of the effects of <device> type contributing to VUR. Values are McNeamar's test results for within-subjects comparisons for participants who received both questions.

%For the between-subjects comparison (i.e., participants who received one question, but not the other), you can do either a chi-square test or Fisher's exact test. Both use a 2 x 2 contingency matrix (i.e., rows are outcomes---upset or not---and columns are conditions---wearable or smartphone). The way to choose between the two tests is based on sample size, generally you use chi-square when there are more than 10-20 samples per cell in the table, but using either is just as valid. For the within-subjects comparisons (i.e., participants received both questions), you would do McNemar's test; which is the within-subjects version of the chi-square test.
